---
title: "Blumatix Consulting"
author: "Philipp Grafendorfer"
date: "21st of October 2017"
output: 
  ioslides_presentation:
    fullscreen: true
    widescreen: true
    css: style.css
    logo: bludeltalogo.png
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Tools, techniques and perception

> - Supervised Learning, Unsupervised Learning
> - Interactive Reporting
> - Interactive Shiny- application on Microsoft R Server
> - Microsoft Azure ML Services
> - R is good for Machine Learning
> - Python is better
> - Feature engineering is key

## Highlights

- Pivoting
- Interactive apps
- Modern algorithm (xgboost)
- Webservice deployment

## Pivoting

1. Import data from database (SQL)
2. Transform Dataframe from long to wide with additional aggregation
3. Present better readable dataframes


## Result of database query
```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(data.table)
df <- fread(input = 'sample_df.csv', select = c(2,3,4), data.table = F)
print(df[1:10,])
```


## Pivot Table with utf-8 issue
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pivot <- fread('user_vs_details.csv')
print(pivot[1:10,1:5])
```


## XGBoost

- Gradient Boosting Tree Algorithm
- Supervised Learning
- Cross Validated results
- Parallelization
- Continued Training
- Free open source
- Fast


## Access xgboost

- R interface as well as a model in the caret package
- Command Line Interface (CLI)
- C++ (the language in which the library is written)
- Python interface as well as a model in scikit-learn
- Julia
- Java and JVM languages like Scala and platforms like Hadoop


## Microsoft Azure ML Webservices

### Hot
- Easy pseudo- wysiwyg training
- Easy webservice implementation
- on-demand computational power

### Not
- No code hands-on, therefore no finetuning
- Limited possibilities in modeling and special libraries


## Links

- <https://www.bludelta.ai/>
- <https://github.com/philippgrafendorfe>
- <https://datasciencesalzburg.slack.com>
- <http://blog.kaggle.com/2017/01/23/a-kaggle-master-explains-gradient-boosting/>



### Thanks for your attention.