---
title: "Blumatix since Februar 2017"
author: "Philipp Grafendorfer"
date: "21st of October 2017"
output: 
  ioslides_presentation:
    fullscreen: true
    widescreen: true
    css: style.css
    logo: bludeltalogo.png
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Tools and techniques

> - R is good for Machine Learning
> - Python 3 is better
> - Supervised Learning, Unsupervised Learning
> - Reporting
> - Interaktive Shiny- Applikation auf Microsoft R Server
> - Azure ML Services

## What matters most?

- Pivoting
- Interactive apps
- Strong testing algorithm (xgboost)
- Webservice deployment

## Pivoting

- Long -> Wide
- Aggregation
- Import data from database

## Wishes become true
```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(data.table)
df <- fread(input = 'test.csv', select = c(2,3,4), data.table = F)
print(df[1:10,])
```

<!-- ```{python, engine.path="C:\Program Files\Anaconda3"} -->
<!-- final = df.pivot_table(index='UserID', columns='DetailID', values='InvoiceID', aggfunc=lambda x: len(x.unique())) -->
<!-- print(final) -->
<!-- ``` -->


## XGBoost

- Gradient Boosting Tree Algorithm
- Supervised Learning
- Cross Validation lies within by definition
- Parallelization
- Continued Training
- Free open source
- Fast


## How to access xgboost

- R interface as well as a model in the caret package.
- Command Line Interface (CLI).
- C++ (the language in which the library is written).
- Python interface as well as a model in scikit-learn.
- Julia.
- Java and JVM languages like Scala and platforms like Hadoop.


## Microsoft Azure ML Webservices

+ Easy pseudo- wysiwyg training
+ Easy webservice implementation
+ on-demand computational power
- No code hands-on


## Links

- <https://www.bludelta.ai/>
- <https://github.com/philippgrafendorfe>
- <https://datasciencesalzburg.slack.com>

